\tool

### 2018-02-08 paper/paper.tex
Intro updates, almost done

\maketitle
\begin{abstract}
Software developers have access to a variety of useful tools designed to increase productivity that are often ignored or undiscovered by potential users. This lack of tool awareness can have dangerous consequences, especially in the software engineering industry. Automated recommendation systems have been created in an attempt to improve software tool discovery, however these systems are still less effective than user-to-user recommendations. To increase awareness of helpful tools, we introduce \textit{\tool}, a novel system which integrates concepts from peer interactions and software development processes to increase discovery of software engineering tools, and found that our approach is useful in making recommendations and improving tool discovery of a static analysis tool to Java developers on open source GitHub projects.
\end{abstract}

@@

Software is becoming more and more prevalent throughout our society. To keep up with the increasing demands for technology, software engineers are making efforts to emphasize \textbf{definition}, or \textit{software quality}. This includes more focus on improving metrics that impact both software producers and consumers, such as functionality, reliability, usability, efficiency, maintainability, and portability~\cite{KitchenhamQualityTarget}. However, despite increased attention to software quality, defects in code remains a persisting and escalating problem.

@@

To prevent production errors and improve code quality, researchers and toolsmiths have created software engineering tools to aid developers in their work. These useful tools provide a variety of functionality to save time and effort for software engineers in programming tasks, such as finding defects, identifying bugs, making large-scale code changes, suggesting fixes, and checking for security vulnerabilities. Research shows that tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, code navigation, and more are effective in preventing defects and improving software quality, ultimately leading to reduced debugging costs and increased developer productivity.

Althouth quality is a primary concern for software producers and consumers, developers often ignore useful tools designed to help improve the quality of their code~\cite{Johnson2013Why}. There are many barriers to tool adoption, but one of primary reason useful tools are underused or ignored is the discoverability barrier, or when users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of awareness can lead to poor code quality and significant amounts of wasted time and money fixing bugs. To improve tool discovery, automated recommendation systems have been created to

%Peer

@@

To help solve the tool discovery problem, we developed \textit{\tool} to automatically recommend useful tools to software developers. We designed our system to make suggestions by integrating characteristics of peer interactions found in previous work as well as concepts from software engineering. \tool contains a unique workflow that runs specific tools and makes customized recommendations to developers on GitHub\footnote{https://github.com}, the most popular code hosting site for collaborative software development. This work seeks to answer the following research questions (RQs): \\

@@

To answer these questions, we evaluate \tool~by recommending the \textsc{Error Prone}\footnote{http://errorprone.info} static analysis tool on open source Java GitHub projects. We observed the frequency of recommendations made and examined how software developers reacted to receiving a suggestion from our system. This research makes the following contributions:

\begin{itemize}
 \item a novel automated recommendation system \tool~that allows researchers to recommend software development tools to GitHub developers, and
 \item an evaluation on the applicability and usefulness of our approach using \textsc{Error Prone}
 \end{itemize}

>>>>

\maketitle
\begin{abstract}
Software developers have access to numerous tools designed to increase productivity by automatically performing development tasks, but these tools are often ignored or undiscovered by programmers. This lack of tool awareness can have dangerous consequences, especially in the software engineering industry. Automated recommendation systems were created to improve tool discovery, however these systems are not as effective as user-to-user recommendations. To increase awareness of helpful development tools, we introduce \textit{\tool}, a novel system that integrates concepts of peer interactions and software engineering practices to increase tool discovery by effectively making recommendations to developers on open source GitHub projects.
\end{abstract}

@@

Software is becoming more and more prevalent throughout our society. To keep up with the increasing demands for technology, software engineers are making efforts to emphasize \textbf{definition}, or \textit{software quality}. Throughout the software development life cycle, more focus is being put on metrics that impact both software producers and consumers such as functionality, reliability, usability, efficiency, maintainability, and portability~\cite{KitchenhamQualityTarget}. However, despite increased attention to software quality, defects in code remains a persisting and escalating problem.

@@

To improve code quality and prevent errors, researchers and toolsmiths have created numerous software engineering tools to aid developers in their work. These tools automatically perform a wide variety of software development tasks to save time and effort for programmers. Research shows that tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, code navigation, and more are beneficial for preventing errors and improving software quality. Ultimately, these useful tools can lead to reduced debugging costs and increased developer productivity.

Althouth quality is a primary concern for software engineers and users, developers rarely use tools designed to improve code~\cite{Johnson2013Why}. There are many barriers to tool adoption, and one of the primary reasons useful tools are underused or ignored is the discoverability barrier, or when users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of awareness for software engineering tools can lead to poor code quality, harmed users, and significant amounts of time and money spent fixing errors. While many automated approaches have been developed to increase knowledge of useful software tools and features, Murphy-Hill and colleagues found that learning about tools from colleagues during normal work activities, or \textit{peer interactions}, is the most effective mode of tool discovery\cite{MurphyHill2011PeerInteraction}.

@@

To help solve the tool discovery problem among software developers, we developed \textit{\tool} to automatically recommend software engineering tools. Our system makes recommendations by integrating characteristics of peer interactions and software engineering practices. \tool~is designed for toolsmiths to increase awareness of their work by automatically running tools and making customized recommendations to developers of GitHub\footnote{https://github.com} projects. This paper seeks to answer the following research questions (RQs): \\

@@

To answer these questions, we evaluated \tool~by recommending \textsc{Error Prone}\footnote{http://errorprone.info}, an open source static analysis tool for Java code. We examined how often recommendations were made and how developers reacted to receiving suggestions from our system. This research makes the following contributions:

\begin{itemize}
 \item a novel system for researchers to recommend software engineering tools on GitHub, and
 \item an evaluation on the effectiveness of \tool~with \textsc{Error Prone}
 \end{itemize}
